Optimal (Multiway) Spatial Joins

### 2024-05-25 msj.tex
yufei

        \item If a $k$-tuple $(r_1, r_2, ..., r_{k-2}, h, v)$ belongs to $\J_1$, then $\bm{t} = (r_1, r_2, ...,$ $r_{k-2})$ belongs to $\J(R_1', R'_2, ..., R'_{k-2})$, and       
        $h \in \dcross_H(\bm{t})$ and $v \in \dcross_V(\bm{t})$.

@@

\begin{lemma} \label{lmm:hv:type2:properties}
    For each $\bm{t} \in \J(R_1, ..., R_{k-3}, H', V)$, we have:
        \myenums{
            \item $\contained_{R_{k-2}}(\bm{t}) \ne \emptyset$.

            \item Denote by $h$ the full segment of $\bm{t}[k-1]$. 
            For any $r_{k-2} \in \contained_{R_{k-2}}(\bm{t})$, the $k$-tuple $(\bm{t}[1], ..., \bm{t}[k-3], r_{k-2}, h, \bm{t}[k])$ belongs to $\J(R_1, ..., R_{k-2}, H, V)$.

            \item If the $k$-tuple $(r_1, r_2, ..., r_{k-2}, h, v)$ belongs to $\J_1$, then $h \in \dcross_H(\bm{t})$ and $v \in \dcross_V(\bm{t})$.
        }
\end{lemma}

>>>>

        \item If a $k$-tuple $(r_1, r_2, ..., r_{k-2}, h, v)$ belongs to $\J_1$, then $\bm{t} = (r'_1, r'_2, ...,$ $r'_{k-2})$ belongs to $\J(R_1', R'_2, ..., R'_{k-2})$, and       
        $h \in \dcross_H(\bm{t})$ and $v \in \dcross_V(\bm{t})$, where $r'_i$ ($i \in [k-2])$ is the trimmed rectangle of $r_i$.

@@

\begin{lemma} \label{lmm:hv:type2:properties}
    All the following statements are true:
    \myenums{
        \item For each $\bm{t} \in \J(R_1, ..., R_{k-3}, H', V)$, we have:

        \myenums{
            \item $\contained_{R_{k-2}}(\bm{t}) \ne \emptyset$.

            \item Denote by $h$ the full segment of $\bm{t}[k-1]$. 
            For any $r_{k-2} \in \contained_{R_{k-2}}(\bm{t})$, the $k$-tuple $(\bm{t}[1], ..., \bm{t}[k-3], r_{k-2}, h, \bm{t}[k])$ belongs to $\J_2$.
        }

        \item If the $k$-tuple $(r_1, r_2, ..., r_{k-2}, h, v)$ belongs to $\J_2$, then $\bm{t} = (r_1, ..., r_{k-3}, h', v)$ belongs to $\J(R_1, ..., R_{k-3}, H', V)$ and        
        $h' \in \contained_{R_{k-2}}(\bm{t})$, where $h'$ is the trimmed segment of $h$.

        \item d
    }
\end{lemma}
